Scalar Feedback based Joint Time-Frequency Precoder Interpolation for MIMO-OFDM Systems

### 2020-04-26 paper/main.tex
Minor fix

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy. 
In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated
using the neighbouring subcarriers using bilinear interpolation
(equivalent to linear interpolation in two dimensions). These
interpolated values are then used to reconstruct the precoding
matrices all together by applying the reverse transformation of
breaking the precoder into independent parameters as given in
Equation~\ref{eq:decompose}. Inorder to improve the precoder estimates 
and interpolation accuracy we walkback to improve the past estimates by interpolating
upon the current estimates. Thus, the approach here is able to exploit the time and frequency correlation jointly to enhance performance.
% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%

>>>>

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy. 
In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values are
then used to reconstruct the precoding matrices all together by
applying the reverse transformation of breaking the precoder into
independent parameters as given in Equation~\ref{eq:decompose}. To
improve the precoder estimates and interpolation accuracy, we ``walk
back'' to improve the past estimates by interpolating using current
estimates (although the current estimates only use data
causally). Thus, the approach here is able to exploit the time and
frequency correlation jointly to enhance performance.
% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%
